Psychological Needs During Intergroup Contact

### 2021-11-21 manuscript.tex
Updates from Overleaf

In this article, we propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and in extension positive outgroup attitudes. Additionally, such needs might even explain the effectiveness of Allport's optimal contact conditions, if these conditions constitute common psychological needs of the interacting individuals. To test this we collected three sets of real-life data from recent immigrants, tracking situational needs, interaction quality, and outgroup attitudes, following their daily interactions with host majority group members.

\section{Psychological Needs in Intergroup Relations}

\faQuestionCircle\ Past research on the mechanisms of Allport's Conditions + research on interaction quality.

\faKeyboard\ We should probably add a short section on past literature that has examined psychological needs in intergroup contact in general \citep[e.g.,][]{Shnabel2008} as well as for particular groups, including migrants \citep[e.g.,][]{Celebi2017}.

\noindent We should probably also include:
\begin{displayquote}
    Psychological needs might “explain the asymmetry of experiences and outcomes in intergroup interactions and identify an essential element for interventions: To achieve truly constructive intergroup relations, it is important that intergroup exchanges meet the psychological needs of both majority- and minority-group members” \\
    \hfill --- \citep[][p. 611]{Dovidio2017}
\end{displayquote}

We probably need to note that there are really good papers on the likely mechanisms of intergroup contact \citep[e.g.,][]{Brown2005}. But they don't discuss Allport's conditions.

Plus, recent work Nurit Shnabel.

\section{The Present Research}
\faKeyboard\ To be written out.

@@

Based on this we formulated four main hypotheses:

@@

\faKeyboard\ all assumptions were fine (see Online Supplementary Materials B).

\section{Appendix A}
\label{app:AppendixA}

The Appendix text goes here.

>>>>

In this article, we propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and in extension positive outgroup attitudes. That is to say, that if someone seeks/wishes to ... . 
Additionally, such needs might even explain the effectiveness of Allport's optimal contact conditions, if these conditions constitute common psychological needs of the interacting individuals. To test this we collected three sets of real-life data from recent immigrants, tracking situational needs, interaction quality, and outgroup attitudes, following their daily interactions with host majority group members.

\section{Intergroup Contact Mechanisms}
\begin{itemize}
    \item theoretical mechanisms (moderator and mediators) \citep[][]{Brown2005}. They don't discuss Allport's conditions(?)
    \item Allport's conditions
    \item interaction quality
\end{itemize}

\section{Psychological Needs in Intergroup Relations}
\begin{itemize}
    \item general \citep[][]{Shnabel2008}. + Nurit's recent papers 
    \item migrants \citep[][]{Celebi2017}
    \item intergroup contact \citep[][]{Dovidio2017}
\end{itemize}

\begin{displayquote}
    Psychological needs might “explain the asymmetry of experiences and outcomes in intergroup interactions and identify an essential element for interventions: To achieve truly constructive intergroup relations, it is important that intergroup exchanges meet the psychological needs of both majority- and minority-group members” \\
    \hfill --- \citep[][p. 611]{Dovidio2017}
\end{displayquote}

\section{Process Data}
\begin{itemize}
    \item retrospective vs. near-time data
    \item need for real-life data
    \item barriers
    \item innovations like 'contact logger' \citep[][]{Keil2020}, and FormR \citep[][]{Arslan2020} make this possible now
\end{itemize}

@@

\section{The Present Research}

\begin{itemize}
    \item aims
    \item shortened hypotheses
    \item analysis strategy
    \item assumptions, materials, preregistration
\end{itemize}

Based on this we formulated four main hypotheses:
\begin{enumerate}
    \item 
    \item
    \item
\end{enumerate}

\section{Appendix A: Hypotheses}
\label{app:AppendixA}

@@
